---
title: 'Experiment 1: Supplementary Analyses'
author: "Bethany Gardner"
date: "3/29/2022"
output: 
  github_document:
    toc: true
    toc_depth: 3
  pdf_document:
    toc: true
    toc_depth: 3
editor_options: 
  markdown: 
    wrap: 72
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(magrittr)
library(tidyr)
library(dplyr)
options(dplyr.summarise.inform = FALSE)
library(lme4)
library(lmerTest)
library(buildmer)
```

# Setup

Load data and select columns used in model. See data/exp1_data_about.txt
for more details.

```{r}
d <- read.csv("../data/exp1_data.csv", stringsAsFactors=TRUE) %>%
  rename("Participant"="SubjID", "Item"="NameShown") %>%
  select(Participant, SubjGender, Condition, GenderRating, Item, He, She, Other)

str(d)
```

Center gender rating for names: Original scale from 1 to 7, with 1 as
most masculine and 7 as most feminine. Mean-centered with higher still
as more feminine.

```{r}
d %<>% mutate(GenderRatingCentered=scale(d$GenderRating, scale=FALSE))
```

Set contrasts for name conditions.

```{r}
contrasts(d$Condition) = cbind("last vs first/full"=c(.33,.33,-0.66), 
                               "first vs full"=c(-.5,.5,0))
contrasts(d$Condition)
```

Subset for gender rating effects (First and Full conditions only).

```{r}
d.FF <- d %>% filter(Condition!="last") 
d.FF$Condition <- droplevels(d.FF$Condition)
contrasts(d.FF$Condition) = cbind("first vs full"=c(-.5,.5)) #add contrast back
contrasts(d.FF$Condition)
```

# Without OTHER responses

The first supplementary analysis tests if excluding OTHER responses
(7.12% of total responses) affects the pattern of results.

```{r}
o <- sum(d$Other) 
o
o/length(d$Other) 
```

Exclude OTHER responses.

```{r}
d.heshe <- d %>% filter(Other==0)

d.FF.heshe <- d.FF %>% filter(Other==0)
```

## Model 1: Condition w/o OTHER

Effect of Name Condition (first name, last name, full name) on
likelihood of a SHE response, as opposed to a HE response, with OTHER
responses excluded. Participant and Item are again included as random
intercepts, with items defined as the unique first, last and first +
last name combinations.

```{r}
m.cond_other <- glmer(She ~ Condition + (1|Participant) + (1|Item), 
                data=d.heshe, family=binomial)
summary(m.cond_other)
```

No differences in results.

## Model 2: Condition \* Name Gender w/o OTHER

Effects of Name Condition (first name, full name) and the first name's
Gender Rating (centered, positive=more feminine) on the likelihood of a
SHE response as opposed to a HE response, with OTHER responses excluded.
In Experiment 1, the Last Name condition does not include any instances
of the gendered first name, so it is not included here. Participant and
Item are again included as random intercepts.

```{r}
m_namegender_other <- glmer(She ~ Condition * GenderRatingCentered + 
                            (1|Participant) + (1|Item), 
                            data=d.FF.heshe, family=binomial)
summary(m_namegender_other)
```

Compared to the main analysis including OTHER responses, the intercept
is trending instead of significant, the gender rating effect the same,
and the small First vs Full effect is no longer significant.

# Quadratic Name Gender Rating

The second supplementary analysis tested the effect of squared name
gender rating, such that larger values meant names with stronger gender
associations (masc or fem), and smaller values meant names with weaker
gender associations.

```{r}
d.FF %<>% mutate(GenderRatingSquared=GenderRatingCentered^2)
```

## Model 3: Quadratic

No quadratic effects.

```{r}
m_namegender_squared <- glmer(She ~ Condition*GenderRatingCentered + 
                              Condition*GenderRatingSquared +
                              (1|Participant) + (1|Item), 
                              d.FF, family="binomial")
summary(m_namegender_squared)
```

# Participant Gender

## Setup/Data Summary

The third supplementary analysis looks at participant gender: if male
participants show a larger bias towards HE responses than non-male
participants.

Participants entered their gender in a free-response box.

```{r}
d %>% group_by(SubjGender) %>% 
  summarise(total=n_distinct(Participant))
```

For this analysis, we exclude participants who did not respond. Because
there are not enough participants to create 3 groups, we compare male to
non-male participants.

```{r}
d.gender <- d %>% filter(SubjGender != "N/A") %>%
            mutate(SubjGenderMale=(ifelse(SubjGender=="male", 1, 0)))

d.gender %>% group_by(SubjGenderMale) %>% 
  summarise(total=n_distinct(Participant))
```

Summary of responses by condition and participant gender.

```{r}
d.gender %<>% mutate(ResponseAll=case_when(
              He==1 ~ "He",
              She==1 ~ "She", 
              Other==1 ~ "Other"))

d.gender.count_responses <- d.gender %>% 
  group_by(Condition, ResponseAll, SubjGenderMale) %>%
  summarise(n=n()) %>%
  pivot_wider(names_from=c(ResponseAll),
              values_from=n) %>%
  mutate(She_HeOther = She / (He+Other),
         She_He = She / He) %>%
  rename("ParticipantGender"="SubjGenderMale") 
d.gender.count_responses$ParticipantGender %<>% recode("0"="Non-male", "1"="Male")

print(d.gender.count_responses)
```

Participant gender is mean centered effects coded, comparing non-male
participants to male participants.

```{r}
d.gender$SubjGenderMale %<>% as.factor()
contrasts(d.gender$SubjGenderMale)=cbind("NM_M"=c(-.5,.5)) 
contrasts(d.gender$SubjGenderMale)
```

Subset First and Full conditions.

```{r}
d.FF.gender <- d.gender %>% filter(Condition!="last")
d.FF.gender$Condition <- droplevels(d.FF.gender$Condition)
contrasts(d.FF.gender$Condition) = 
  cbind("first vs full"=c(-.5,.5)) #add contrast back
contrasts(d.FF.gender$Condition)
```

## Model 4: Condition \* Participant Gender

Effect of Name Condition (first name, last name, full name) and
Participant Gender (non-male vs male) on likelihood of a SHE response,
as opposed to a HE response or OTHER response. Participant and Item are
again included as random intercepts.

```{r}
m_cond_subjgender <- glmer(She ~ Condition * SubjGenderMale + 
            (1|Participant) + (1|Item), 
            data=d.gender, family=binomial)
summary(m_cond_subjgender)
```

Male participants are less likely to respond SHE overall than non-male
participants, but this is not significant after correcting for multiple
comparisons. Neither interaction with Condition is significant.

## Model 5: Condition \* Name Gender \* Participant Gender

Effects of Name Condition (first name, full name), the first name's
Gender Rating (centered, positive=more feminine), and Participant Gender
(non-male vs. male) on the likelihood of a SHE response as opposed to a
HE or OTHER responses. In Experiment 1, the Last Name condition does not
include any instances of the gendered first name, so it is not included
here. The model with random intercepts does not converge with glmer, but
does when using buildmer to find the maximal model (?).

```{r}
m_cond_name_subjgender <- buildmer(formula=
            (She ~ Condition * GenderRatingCentered * SubjGenderMale + 
            (1|Participant) + (1|Item)), 
            data=d.FF.gender, family=binomial, direction=c("order"))
summary(m_cond_name_subjgender)
```

-   Participant Gender: n.s.

-   Condition (First vs Full) \* Participant Gender: There is a larger
    difference between the First and Full Name conditions for male
    participants (see means above), but this is n.s. after correcting
    for multiple comparisons.

-   Name Gender \* Participant Gender: There is a stronger effect of the
    first name gender rating for male participants, but this is n.s.
    after correction for multiple comparisons.

-   Condition (First vs Full) \* Name Gender \* Participant Gender:
    trending
