---
title: 'Experiment 1: Main Analyses'
author: "Bethany Gardner"
date: "3/29/2022"
output: 
  github_document:
    toc: true
    toc_depth: 3
  pdf_document:
    toc: true
    toc_depth: 3
editor_options: 
  markdown: 
    wrap: 72
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(magrittr)
library(tidyr)
library(dplyr)
options(dplyr.summarise.inform = FALSE)
library(lme4)
library(lmerTest)
```

# Setup

Load data and select columns used in model. See data/exp1_data_about.txt
for more details.

```{r}
d <- read.csv("../data/exp1_data.csv", stringsAsFactors=TRUE) %>%
  rename("Participant"="SubjID", "Item"="NameShown") %>%
  select(Participant, Condition, GenderRating, Item, He, She, Other)
str(d)
```

Center gender rating for names: Original scale from 1 to 7, with 1 as
most masculine and 7 as most feminine. Mean-centered with higher still
as more feminine.
```{r}
d %<>% mutate(GenderRatingCentered=scale(d$GenderRating, scale=FALSE))
```

Set contrasts for name conditions.
```{r}
contrasts(d$Condition) = cbind("last vs first/full"=c(.33,.33,-0.66), 
                               "first vs full"=c(-.5,.5,0))
contrasts(d$Condition)
```

Subset for gender rating effects (First and Full conditions only).
```{r}
d.FF <- d %>% filter(Condition!="last") 
d.FF$Condition <- droplevels(d.FF$Condition)
contrasts(d.FF$Condition) = cbind("first vs full"=c(-.5,.5)) #add contrast back
contrasts(d.FF$Condition)
```

# Data summary

Responses by condition.
```{r}
d %<>% mutate(ResponseAll=case_when(
       He==1 ~ "He",
       She==1 ~ "She", 
       Other==1 ~ "Other"))

d.count_responses <- d %>% group_by(Condition, ResponseAll) %>%
  summarise(n=n()) %>%
  pivot_wider(names_from=ResponseAll,
              values_from=n) %>%
  mutate(She_HeOther = She / (He+Other),
         She_He = She / He)

print(d.count_responses)
```

-   First name condition has second-most SHE responses
-   Full name condition has most SHE responses
-   Last name condition has fewest SHE responses

# Model 1: Condition

Effect of Name Condition (first name, last name, full name) on
likelihood of a SHE response, as opposed to a HE or OTHER response.
Participant and Item are included as random intercepts, with items
defined as the unique first, last and first + last name combinations.
Because the condition manipulations were fully between-subject and
between-item, fitting a random slope model was not possible.

```{r}
m.cond <- glmer(She ~ Condition + (1|Participant) + (1|Item), 
            data=d, family=binomial)
summary(m.cond)
```
Fewer SHE responses overall. First+Full have more SHE responses than
Last. Full has more SHE responses than First (n.s. but matches ratios).

# Model 2: Condition \* Name Gender

Effects of Name Condition (first name, full name) and the first name's
Gender Rating (centered, positive=more feminine) on the likelihood of a
SHE response, as opposed to a HE or OTHER response. In Experiment 1, the
Last Name condition does not include any instances of the gendered first
name, so it is not included here. Participant and Item are again
included as random intercepts.

```{r}
m.namegender <- glmer(She ~ Condition * GenderRatingCentered + 
            (1|Participant) + (1|Item), 
            data=d.FF, family=binomial)
summary(m.namegender)
```

More SHE responses as first names become more feminine. Difference
between First and Full is now significant (as compared to condition-only
model).
